The Astropy Project

### 2017-12-06 main.tex
Address concerns in #50
Remove wording that requires Python specific coding knowledge ("decorator")
and add a general "who's the audience for this article" to the intro.

Fixes #50

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
% heavily edited by Adrian PW - let me know if you want to revert anything!
All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
for astronomical tasks: from scripts that enable individual scientific research to software packages for small collaborations to data reduction pipelines for survey operations.
Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world? I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'. For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
%\inlinecomment{Perry G}{Agreed}

@@

@@

\subsubsection{Defining functions that require quantities}
        When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator,
        \texttt{quantity\_input()}, that does this verification automatically.

@@

Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}. A model is instantiated by passing in values (scalars or arrays) for its parameters. A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints. The value and constraints can be updated by assignment. Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values. Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials). Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules. A model is evaluated by calling it as a function.

Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise. This is a settable property; i.e. a model instance can be assigned as inverse to another model. For example, a polynomial model can be assigned as an inverse to another polynomial model.

@@

\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate. This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.

@@

\subsubsection{Creating New Models}

New model classes can be created in two ways:
\begin{enumerate}
   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
\end{enumerate}

>>>>

\section{Introduction} \label{sec:intro}
All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
for astronomical tasks: from scripts that enable individual scientific research to software packages for small collaborations to data reduction pipelines for survey operations.
Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

@@

This article is not intended as an introduction to \astropypkg, nor does it replace the \astropypkg documentation. Instead, it describes the way the \astropy community works and organizes and the current state of the \astropypkg package.

@@

\subsubsection{Defining functions that require quantities}
        When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
        that can perform this varification automatically to avoid repetitive
        code.

@@

Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}. A model is constructed by passing in values (scalars or arrays) for its parameters. A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints. The value and constraints can be updated by assignment. Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values. Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials). Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules. A model is evaluated by calling it as a function.

Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise. This is a settable property; i.e. a model can be assigned as inverse to another model. For example, a polynomial model can be assigned as an inverse to another polynomial model.

@@

\package{astropy.modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.

@@

\subsubsection{Creating New Models}
If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways. The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows to extend the build-in model class with arbitrary code.
